---
title: "Readme"
output: github_document
---

Package used for a survey including pairwise comparison (left-right in our case)

## Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse)
devtools::load_all()
```

## TODO

### Match Play

+ Pre-Survey to register through google-doc
  + Name 
  + Mail
  + Partei
  + Paiment preferences
  
+ Skype Meeting agenda for survey explanation

+ Objective: 
  + 400 to 500 comparisons 2-3 Stunden (70€)
  + Amazon Gutschein/Paypal/Überweisung

+ Wie wollen wir den Teilnehmer kontaktieren? 
  + Mail
  + Twitter



## To discuss

+ User Management
+ Phrasing
+ What par_anal argument should we use? (use to analytically reduce the pairs)
+ What test should we still run? 

+ How many participants? (#/party)
+ How much do we pay them? (depending on how much time they need?)
+ How do we pay them? 


## Main 

```{r}
party <- "SPD"

# This initialises the database, use argument force to overwrite existing database
con <- init_db(user = "ben", path = "data/mp.db", force = T)

# Extracting all potential pairs of MP
pair_mp <- get_pair_matrix(party = party)


# Get a new pair, which has not been coded yet and which does not include "not known" mps
d <- get_new_pair(user = "ben", con = con) %>% glimpse

# Add one of the name to the don't know table ("dk")
add_dont_know(user = "ben", pageid = d$pageid_1, name = d$name_1, party = d$party_1)



# Add comparison, more_left should be either : -1 (1 > 2) ; 0 (same position) ; 1 (2 > 1)
add_comparison(user = "ben", pageid_1 = d$pageid_1, pageid_2 = d$pageid_2, 
               name_1 = d$name_1, d$name_2,
               more_left = 1, 
               time = lubridate::now(), party = party)

# Get the don't knows
dks <- con %>% tbl("dk") %>% glimpse
# Get the comparisons
comps <- con %>% tbl("com") %>% glimpse
```

```{r}
pairwiseR::mp %>%
  count(party) %>%
  mutate(comparisons = n * 20)
```


## MP Database

```{r, eval=F}
data <- legislatoR::get_core("deu") %>%
  left_join(legislatoR::get_political("deu")) %>%
  left_join(legislatoR::get_office("deu")) %>%
  left_join(legislatoR::get_traffic("deu")) %>%
  left_join(legislatoR::get_portrait("deu"))

# names(data)

mp <- data %>% 
  filter(session == 18) %>%
  select(pageid, name, party, date, traffic, image_url) %>%
  group_by(pageid, name, party, image_url) %>%
  summarise(trafic = median(traffic)) %>%
  ungroup %>%
  mutate(party = case_when(
    party %in% c("CDU", "CSU") ~ "CDU/CSU", 
    party == "BÜNDNIS 90/DIE GRÜNEN" ~ "GRUENE", 
    party ==  "DIE LINKE" ~ "PDS/LINKE", 
    party == "none" ~ NA_character_, 
    T ~ party
  )) %>%
  group_by(party) %>%
  arrange(-trafic) %>%
  slice(1:100) %>%
  mutate(most_popular = ifelse(1:n() %in% 1:10, T, F)) %>%
  ungroup %>%
  glimpse

# usethis::use_data(mp, overwrite = T)
# mp
```

```{r}
mp_data <- get(load("data/mp_lp19.Rdata"))
mp <- mp_data %>%
  transmute(pageid = 1:n(), 
         name = str_trim(name), 
         party = party, 
         image_url = img_link, 
         traffic = traffic)
  
usethis::use_data(mp, overwrite = T)
```


